---
title: "My R Markdown Primer"
author: "Jacob Studstill"
date: "2025-11-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

The markdown in R contains plain text as well as chunks of R code. I use markdowns when I am completing labs in my other R courses because the instruction between the R chunks instructs me what to do and the R chunks is where I write the R. I like this more than having to tab back and forth between the instructions and my code.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
a <- sample(1:100, 1)
b <- sample(1:100, 1)

latexProblem <- paste0("$", a, " + ", b, " = \\, ?$")

latexProblem
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
library(ggplot2)

ggplot(cars, aes(x = speed, y = dist)) +
  geom_point() +
  labs(title = "Speed vs Distance To Stop",
       x = "Speed",
       y = "Stopping Distance")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
